%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Cies Resume/CV
% LaTeX Template
% Version 1.1 (20/7/14)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Cies Breijs (cies@kde.nl)
% https://github.com/cies/resume with extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt,a4paper]{article} % Font size (10-12pt) and paper size (a4paper, letterpaper, legalpaper, etc)

\include{structure} % Include structure.tex which contains packages and document layout definitions

\hyphenation{Some-long-word} % Specify custom hyphenation points in words with dashes where you would like hyphenation to occur, or alternatively, don't put any dashes in a word to stop hyphenation altogether

\begin{document} 

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\maintitle{Charles Sizer}{}  % Your name and date of birth or subtitle

\noindent\href{mailto:charlie@sizer.tech}{charlie@sizer.tech}\bull % Your email address
\textsmaller{+}1 (630) 452-8359\bull %smith01 \textit{(Skype)}\bull % Your phone number(s) and Skype username
%\href{http://www.johnsmith.com}{www.johnsmith.com}\\ % Your URL
520 Clifton Ave\bull Sheboygan, WI%\bull%\bull Country % Your address

\spacedhrule{0.9em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	SUMMARY SECTION
%----------------------------------------------------------------------------------------

\roottitle{Summary} % Root section title

\vspace{-1.3em} % Reduce whitespace after the Summary heading and the two-column content

\begin{multicols}{2}  % Start a two-column layout
\noindent \textit{Mathematician. Engineer. Analyst. Manager.}\\\\
\emph{Objective: }Use my start up business experience to obtain a challenging position where I will use my modeling, creative problem-solving, and analytical skills to drive positive business outcomes.  Eager to put skill set to work for local Sheboygan employer.   \\
\\\\
\noindent 
I am a mathematician. I applied my skills to food-industry research and development, operations, and management where, at a succession of bold start-ups, I honed my business understanding. For nearly fifteen years, I was the go-to when complicated problems needed sophisticated spreadsheets to make them comprehensible. I worked with senior leaders to capture business data and inform company strategies and decisions.
%I solve complex problems by building models to evaluate steady-state and transient phenomena.
%I am a master at excel; I've even had requested features added by Microsoft. 

\end{multicols}

\spacedhrule{0.5em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\roottitle{Experience} % Top level section 
\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{http://www.boomboxbeverage.com}{Boombox Beverage LLC}}
{\textsc{Skokie, IL}} {

\headedsubsection % Job title entry for the current employer
{Director of Food Safety and Quality}%title
{July 2020 - Present} %employment dates
{\bodytext{
Selectively hired during start-up to establish a food safety program in compliance with low-acid foods regulation, achieve Safe Quality Food (SQF) certification, and develop new capabilities to extend the business.

\emph{Accomplishments}
\begin{itemize}
\item Major contributor to company strategies and decision-making; drove insights into food safety problems impacting decisions and business performance 
\begin{itemize}
\item Created business policies and the tools to implement them (pillar of organization), assuring regulatory compliance and business continuity
\item Designed and proposed dashboards to tell a story through data to keep leadership informed
\item Learned/applied JavaScript v8 to automate business workflows in google docs
\item Generated/analyzed production reports, identified areas of improvement, and produced actionable reports (issued Corrective Action Requests) daily, keeping company in compliance with regulatory procedures
\item Driving force behind SQF level 1 certification effort 
\end{itemize}

\item Designed and implemented Food Safety Program for a startup low acid canned food facility 
\begin{itemize}
\item Developed and implemented Food Safety Plan (HARPC) for all products. 

\item Hired, trained and, and managed highly regarded Quality Team 
\end{itemize}

\item Launched three new products for a national brand, managing and prioritizing concurrent projects, while responding to changing business needs 
    \begin{itemize}
    \item Developed new programs and procedures in a highly ambiguous environment 
    \item Gathered/analyzed statistical data on machine performance to define customer specification
    \end{itemize}
\end{itemize}
}}}
\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{http://www.kda-auto.com}{KD Automation}}
{\textsc{Jackson, WI}} {

\headedsubsection % Job title entry for the current employer
{Systems Integration Manager}%title
{July 2019-Feb 2020} %employment dates
{\bodytext{
Retained to fill gap in cross-disciplinary team to design, develop, creative problem solve, and program a progressive assembly line.

\emph{Accomplishments}
\begin{itemize}
\item Ventured into a different work environment under new management to bring change and apply programming skills
\item Implemented a systematic method for programming with anticipation of future needs/developments  
\item Learned/applied Beckhoff coding environment, a new platform, for real-time automation 
\item Applied skill to create schematics/BOM/panel layout, assist with electrical panel builds, program PLCs, HMIs, robots, camera and other automation devices and to commission machines 
\end{itemize}
}}}

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{http://www.dairyv.com}{Dairyvative Technologies}}
{\textsc{Reedsburg \& Sheboygan, WI}} {

\headedsubsection % Job title entry for the current employer
{Director of Technology} %title
{2013 - Oct 2018} %employment dates
{\bodytext{
Sr Manager responsible for commercialization of a novel dairy product at a tech start-up in a highly parallel and self-motivating setting. Managed product development, processing equipment, integration, controls systems, regulatory compliance, and intellectual property. Designed, built, programmed, and managed the first all-digital dairy processing plant in Wisconsin.  

%}} %employment description
\emph{Accomplishments }
%\headedsubsection
\begin{itemize}

\item Developed new technology for milk preservation with a model-based approach 
    \begin{itemize}
    \item Designed and built commercial-scale prototype based on theory; then reduced theory to practice
    \item Iteratively improved efficiency, reliability, quality, and safety by leveraging use of historical process data (especially loss-of-control postmortems) which provided insight into problems
    \item Investigated complex viscosity phenomena of the product by designing multivariate experiment and using scientific computing tools to analyze the data.  
    \item Compiled complex results into spreadsheets and graphs that made business decisions intuitive.  
    \end{itemize}


\item Commercialized standards compliant milk preservation process 
    \begin{itemize}
    \item Led a team of seven through design and build of state-of-the-art food-grade production facility 
    \item Designed custom batching, heat treating, and packaging solution for the process 
    \end{itemize}

\item Initiated and drove plant efficiencies on proof-of-concept processing lines with automated production systems integrated with upper levels of business logic 
    \begin{itemize}
    \item Developed and deployed an industry leading SCADA system which reduced labor requirements by 75\%
    \item Gathered and analyzed process data from across the process system to provide insights into complex product interactions with equipment and optimize production 
    \item Eliminated paper records, reduced compliance burden, created real-time dashboards and quick read reports allowing equipment operators and management to quickly identifying problems and minimized downtime
    \item Developed mechanisms for compliance with digital record keeping regulations (21CFR11)  
    \end{itemize}

\item Used quantitative analysis to inform company strategies and decision-making 

\begin{itemize}
    \item Developed interactive spreadsheet to help production, sales and management with complicated concentration and volume conversions. Built interactive Production Calculator to handle all probable products, calculate production requirements, and provide actionable business feedback on cost and feasibility
%    \item Modeled system performance and provided analysis of 
    \item Dedication to correct mathematical modeling and the qualitative and quantitative analysis of failed runs delivered the appropriate equipment and process design. 
\end{itemize}
\end{itemize}
}
}
}
%------------------------------------------------
\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{http://www.cambrooke.com}{Cambrooke Foods} (now a division of \href{https://www.ajinorthamerica.com/}{Ajinomoto})}
{\textsc{Ayer, \acr{MA}}} {

\headedsubsection % Job title entry for the current employer
{Product Development Specialist}
{2012-2015}
	{
\bodytext{Designed, assembled and commissioned hot-fill and aseptic beverage processing lines for a medical foods company.  }
\emph{Accomplishments }
\begin{itemize}
\item Member of leadership team managing \$5MM facility build-out to produce enteric nutrition products. 
\item Employed data analysis to inform company decisions 
    \begin{itemize}
    \item Generated nutrition reports to formulate and refine medical food products to meet exacting guidelines for enteric nutrition 
    \item Used mathematical analysis and modeling to design process to gently sterilize protein and maximize shelf-life 
    \item Forecast sales to plan production and maximize returns on warehouse space 
    \end{itemize}

\end{itemize}
	}
}
%------------------------------------------------

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{http://}{Pilot Aseptic}}
{St. Charles, IL} {

\headedsubsection % Job title entry for the current employer
{Technician}
{June 2010 - 2012}
{\bodytext{Operated and maintained test-scale beverage processing equipment and utilities.  Researched and conducted processing trials on a wide variety of products.
\begin{itemize}
\item Analyzed magnetic moment data to infer heat penetration into particles and created numerical heat-penetration model used by Pepsi Co. through present day  
\item Extensive on-the-fly trouble shooting of Alfa Laval VTIS \& FLEX systems 
\end{itemize}
}
}}
%------------------------------------------------

%\begin{center}
%\textit{Please refer to \href{http://www.linkedin.com/in/ciesbreijs}{my Linkedin profile} for the complete list of work experiences along with recommendations.}
%\end{center}

%------------------------------------------------

\spacedhrule{-0.2em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\roottitle{Education} % Top level section

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{Illinois Institute of Technology}
{\textsc{Chicago, IL}} {

\headedsubsection % Job title entry for the current employer
{Applied Mathematics}
{2004 -- 2007}
{\bodytext{Focused on discreet methods}}}

\spacedhrule{0.5em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\roottitle{Skills \& Certifications} % Top level section

\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
{Technical specialties:}
{Networking. Python (NumPy, SciPy and Pandas), \textit{Ignition!}.  Familiar with SQL, ZPL, Git, \LaTeX, Modbus and Ethernet/IP . Advanced Excel skills.
Technologies used:  Modbus RTU, 4-20mA loops, PLC ladder logic, Modbus TCP/RTU, Ethernet/IP, ZPL, Jython scripting, SQL, Java, Python (Pandas, MatPlotLib, and SciPy), CentOS, and BSD. }
\inlineheadsection
{Certifications:}
{PCQI, HACCP, BPCS}

%------------------------------------------------

%\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
%{Natural languages:}
%{Dutch \textit{(mother tongue)}, English \textit{(full professional proficiency)}, German \textit{(limited working proficiency)}, French \textit{(elementary proficiency)} and Mandarin Chinese \textit{(beginner)}.}

%------------------------------------------------

\spacedhrule{1.6em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	Patents SECTION
%----------------------------------------------------------------------------------------

\roottitle{Patents} % Top level section

%\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
\begin{itemize}
\item[] Sizer, C.E.  and Sizer, C.E. IV.  Method and Apparatus for sterilizing containers.   US Patent 7,481,974 issued 27 January 2009.
\item[] Sizer, C.E. and Sizer, C.E. IV.   Method and Apparatus for heating and dispensing sterile product.   US Patent 7,595,470 issued 29 September 2009.
\item[] Sizer, C.E. and Sizer, C.E. U.S. Patent Application on Process for Making a Beverage Concentrate with a Low Concentration of Nucleation Sites.
\end{itemize}

%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\roottitle{Interests} % Top level section

\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
{Non-exhaustive and in alphabetical order:}
{cooking, computer security, hiking, kayaking, machine learning,  rocket science, space exploration, sustainability}
%----------------------------------------------------------------------------------------

\end{document} 